---
title: "TN school districts in R"
author: "Jake"
date: "11/16/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

```{r}
library(tidyverse)
```
```{r}
districts=read.csv('~/data_science/r_solo-jcrando/data/districts.csv')
```
```{r}
districts %>% 
  select(-system) 
```

```{r}
districts %>% 
  filter(alg_1>=80, eng_1>=80)
```
there are 13 districts with alg and eng 1 of above 80%

```{r}
districts %>% 
  filter(alg_1 <50| eng_1<50)
```
8 schools are below 50 percent in alg_1 or eng_1

```{r}
districts %>% 
  summarize(min(grad, na.rm=TRUE))
```
the lowest gradution rate seems to be 11.1 for Tenn school for Blind
```{r}
districts %>% 
  arrange(grad)
```
```{r}
districts %>% 
  arrange(desc(dropout))
```
Achievement school district has the highest dropout rate at 27.6

```{r}
districts %>% 
  filter(region=='Mid Cumberland') %>% 
  arrange(desc(act_composite))
```

```{r}
library(ggplot2)
```

```{r}

ggplot(districts, aes(x=grad)) + geom_histogram()
```
```{r}
ggplot(districts, aes(x=grad)) + geom_histogram()
```
the distribution is left skewed

```{r}
ggplot(districts, aes(x=alg_1, y=alg_2))+ geom_point()
```
there seems to be a positive correlation with proficiency in one and the other
```{r}
ggplot(districts, aes(x=alg_1, y=alg_2))+ geom_point()+facet_wrap(~region)
```
the positive correlation seems to go drop in the southeast and there is a point that is unaccounted for for region

```{r}
ggplot(districts, aes(x=region, y= enrollment))+ geom_col()
```
mid cumberland has the highest enrollment, and northwest has the lowest



```{r}
districts %>% 
  select(enrollment, region) %>% 
  filter(is.na(enrollment))
  
```
memphis, upper cumberland, east tn all have na's

```{r}
districts %>% 
  drop_na(grad) %>% 
  summarize(mean(grad))
```

mean graduation is 90.04, there are very different populations sizes in the different regions

```{r}
districts %>% 
  drop_na(grad, enrollment) %>% 
  summarize(weighted.mean(grad, enrollment))
```
the weighted mean is 87.26 which makes since given that some of the regions with the highest enrollment have lower grad rates, in the 70s



```{r}
notn<-districts %>% 
  filter(system_name!='State of Tennessee') 
ggplot(notn, aes(y=enrollment, x=region))+ geom_boxplot()
```

memphis has one crazy high enrollment outlyer

```{r}
notn<-districts %>% 
  filter(system_name!='State of Tennessee') 
ggplot(notn, aes(y=grad, x=region))+ geom_boxplot()
```
all the medians are pretty close

16)in the grad-rgeion boxplot, all of the medians look like they are over the average, but given some of the outliers and given that those outliers may also represent the very high enrollment outliers on the enrollment- region graph, that may make sense.

```{r}
districts %>% 
  drop_na(alg_1, alg_2) %>%
  mutate(alg_difference= alg_1-alg_2) %>% 
  select(system_name, alg_difference) %>% 
  arrange(alg_difference)
```
Pickett county has the largest drop

```{r}
notn<-districts %>% 
  filter(system_name!='State of Tennessee') %>%
  drop_na(alg_1, alg_2) %>%
  mutate(alg_difference= alg_1-alg_2)
ggplot(notn, aes(x=alg_difference))+ geom_histogram()
```

```{r}
districts %>% 
  drop_na(alg_1, alg_2) %>%
  mutate(alg_difference= alg_1-alg_2) %>% 
  select(system_name, alg_difference) %>% 
  filter(alg_difference<0)
```
there are 18 with negative numbers, mean that they had a higher proficiency in alg-2 than alg_1.  18 out of 118 or 15%


```{r}
districts %>% 
  drop_na(eng_2, eng_3) %>%
  mutate(eng_difference= eng_2-eng_3) %>% 
  select(system_name, eng_difference) %>% 
  arrange(eng_difference)
```

the drop off is even more severe with english
18)
```{r}
districts<- districts %>% 
 mutate(null_counts= apply(X= is.na(districts),MARGIN= 1, FUN= sum))
  view()
```
```{r}
districts %>% 
  arrange(desc(null_counts)) %>% 
  view()
```
west tn school for the deaf has the largest number of missing values
many schools that have a lot of missing data are missing grad, dropout, act, eng, alg, and most subjects, but have demographics info

19)

```{r}
install.packages('corrr')
```

```{r}
library(corrr)
```

```{r}
dis_corr<-districts %>% 
  select(alg_1:dropout) %>% 
  correlate() %>% 
  select(term, grad) %>% 
  
  view()
```

```{r}
ggplot(dis_corr, aes(x=grad, fill=term))+ geom_bar(na.rm=FALSE)+coord_flip()
```
high performance in biology and science correlate with higher graduation
